---
title: "Vignette for Bureau of Meteorology"
author: "Ebony Jones, Andrew Robinson, Kate Saunders and Adam Sparks"
date: "22 April 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This vignette is designed to outline mehods for accessing Bureau of Meteorology station data and the Australian Water Availability Project (AWAP) gridded datasets. The rnoaa package has Australian station data from the Global Historical Climatology Network (GHNC), for details see (https://www.ncdc.noaa.gov/data-access/land-based-station-data/land-based-datasets/global-historical-climatology-network-ghcn) .
# Outline:

### Installation

As some of the needed functionality is still in active development and the rnoaa package needs to be downloaded directly from github instead of Cran.

```{r, echo = T, eval = F}
# devtools::install_github("rOpenScieLabs/rnoaa")
devtools::install_github("hrbrmstr/rnoaa")
library(rnoaa)
```

### What station data is available?

Currently available through the GHDN dataset are 16420 unique station names. The data types availabe for these stations are:

<!-- ```{r, echo = T} -->
<!-- unique(oz_stations$element) -->

<!-- Data type | Description -->
<!-- ------------- | ------------- -->
<!-- PRCP | Stuff -->
<!-- DAPR | Stuff  -->
<!-- DWPR | Stuff  -->
<!-- MDPR | Stuff -->
<!-- TMAX | Stuff -->
<!-- TMIN | Stuff -->
<!-- DATX | Stuff -->
<!-- MDTX | Stuff -->
<!-- DATN | Stuff -->
<!-- MDTN | Stuff -->
<!-- TAVG | Stuff -->
<!-- SNWD | Stuff -->

<!-- ``` -->


* what types of data are availabe, PRCP TMAX etc
* where it is available - visualise the locations of available data (temp, rainfall) Kate's got code to do that in leaflet
* ANDREW - can also search for metadata directly from the bureau of meteorology portal using the following function, this data can be downloaded from the api

#### How to get the data:
* how to search for a location (radius search)
* date range

#### How to read the data 
* give a plotted example  (rain/temp)

#### Add some notes about differences /quality

## Create a new section about AWAP data

#### FOR ADAM
* write about AWAP code from Ivan
* write about masking
* write about catchments
